\documentclass[a4paper]{article}
\usepackage{lmodern}
\usepackage{verbatim}
\usepackage{setspace}
\makeatletter
\def\pkginfo#1 #2 #3\relax{%
\def\filedate{#1}%
\def\fileversion{#2}%
}
\expandafter\expandafter\expandafter\pkginfo\csname ver@setspace.sty\endcsname\relax
\makeatother
\title{The setspace Package\thanks{Currently maintained by David Carlisle and others at\\\texttt{https://github.com/latex-package-repositories/setspace/issues}}}
\date{\filedate}
\author{Geoffrey Tobin\and Robin Fairbairns}
\begin{document}

\maketitle

 Usage:

\begin{verbatim}
                \documentclass[...]{...}
                \usepackage{setspace}
\end{verbatim}


         This package (originally based on the \texttt{doublespace} \LaTeX\,2.09 style
         option (package),  created by Stephen Page)
         provides commands and environments for doing double and
         one-and-a-half spacing based on the font size.

         Single spacing is the default.

         The commands \verb|\singlespacing|, \verb|\onehalfspacing|, and
         \verb|\doublespacing|, are for use in the preamble to set the overall
         spacing for the document.  If a different spacing is required then
         the \verb|\setstretch{baselinestretch}| command can be used in the
         preamble to set the baselinestretch appropriately.  The default
         spacing with this style option is single spacing.

         Three environments, \verb|singlespace|, \verb|onehalfspace|,
         and \verb|doublespace|, allow the spacing to be changed
         within the document.  Both the \verb|onehalfspace| and
         \verb|doublespace| environments are intended to increase the
         spacing, so the \verb|onehalfspace| environment should not be
         used in a double spaced document.

         If an increased spacing different from one-and-a-half or
         double spacing is required then the spacing environment can
         be used.  The \verb|spacing| environment takes one argument
         which is the larger baselinestretch to use, e.g.,\\
         \verb|\begin{spacing}{2.5}|.

         \verb|\footins| is adjusted in the same wayas \verb|\parskip|.


\clearpage
\addtolength\textwidth{100pt}
\addtolength\oddsidemargin{-70pt}
\setlength\columnseprule{1pt}
\setlength\columnsep{10pt}
\twocolumn
\tiny
\verbatiminput{setspace.sty}

\end{document}
